Tables

### 2020-11-11 tables.Rmd
update to ego barcharts

library(kableExtra)
library(tidyverse)
library(ggplot2)
```

@@

```{r, fig.width=3.5, fig.height=3}
ego_df <- readRDS('./assets/tables/table_ego_privu.RDS')
univ_order <- (ego_df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University

plot_characteristic <- function(df, type, characteristics) {
  sub_df <- df %>% select(University, characteristics) %>%
    gather(key, value, characteristics) %>%
    mutate(value = parse_number(value))

  # colors <- sub_df$color[order(sub_df$University)]

  sub_df$University <- factor(sub_df$University, levels = rev(univ_order))

@@

plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))
```

>>>>

library(kableExtra)
library(tidyverse)
library(ggplot2)
library(gridExtra)
```

@@

```{r, fig.width=3.5, fig.height=3}
plot_characteristic <- function(df, type, characteristics) {
  sub_df <- df %>% select(University, characteristics) %>%
    gather(key, value, characteristics) %>%
    mutate(value = parse_number(value))

  # colors <- sub_df$color[order(sub_df$University)]
  univ_order <- (df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University  
  sub_df$University <- factor(sub_df$University, levels = rev(univ_order))

@@

type_vec <- c('privu', 'pubu')

for (i in 1:length(type_vec)) {
  ego_df <-readRDS(file.path('.', 'assets', 'tables', str_c('table_ego_', type_vec[i], '.RDS')))

  pdf(file.path('.', 'assets', 'figures', str_c('ego_network_figure_', type_vec[i], '.pdf')), paper = 'a4r')
  par(mfrow=c(2, 2))

  a <- plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
  b <- plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))

  grid.arrange(a, b, c, d, nrow=2, ncol=2)
  dev.off()

  # Need to use print() for ggplot inside loop in order for it to appear
  # https://stackoverflow.com/a/15678596/6373540
  print(a)
  print(b)
  print(c)
  print(d)
}
```
